\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2022-03-31 doc/USER_MANUAL/11_graphics.tex

When running xspecfem3D with the
\texttt{\small MOVIE\_VOLUME}
flag turned on, the code outputs several files in \texttt{\small LOCAL\_PATH}
specified in the main \texttt{\small Par\_file},
e.g. in directory \texttt{\small OUTPUT\_FILES/DATABASES\_MPI}.
The output is saved by each processor at the time interval specified
by
\texttt{\small NTSTEP\_BETWEEN\_FRAMES}.
For all domains,
the velocity field is output to files:
{\small
\begin{verbatim}
proc??????_velocity_X_it??????.bin
proc??????_velocity_Y_it??????.bin
proc??????_velocity_Z_it??????.bin
\end{verbatim}
}
\noindent
For elastic domains, the divergence and curl taken from the velocity field,
i.e. $\nabla\cdot{\bf {v}}$ and $\nabla\times{\bf {v}}$, get stored
as well:
{\small
\begin{verbatim}
proc??????_div_it??????.bin
proc??????_curl_X_t??????.bin
proc??????_curl_Y_it??????.bin
proc??????_curl_Z_it??????.bin
\end{verbatim}
}
\noindent
The files denoted \texttt{\small proc??????\_div\_glob\_it??????.bin} and
\texttt{\small proc??????\_curl\_glob\_it??????.bin}
are stored on the global points only, all the other arrays are stored
on all GLL points. Note that the components X/Y/Z can change to E/N/Z
according to the
\texttt{\small SUPPRESS\_UTM\_PROJECTION}
flag (see also Appendix~\ref{cha:Coordinates} and \ref{cha:channel-codes}).

>>>>

When running xspecfem3D with the
\texttt{\small MOVIE\_VOLUME}
flag turned on, the code outputs several files in \texttt{\small LOCAL\_PATH}
specified in the main \texttt{\small Par\_file},
e.g. in directory \texttt{\small OUTPUT\_FILES/DATABASES\_MPI}.
The output is saved by each processor at the time interval specified
by
\texttt{\small NTSTEP\_BETWEEN\_FRAMES}.
For all domains,
the either the velocity or displacement field is output to files (depending on setting \texttt{SAVE\_DISPLACEMENT}):
{\small
\begin{verbatim}
proc??????_velocity_X_it??????.bin
proc??????_velocity_Y_it??????.bin
proc??????_velocity_Z_it??????.bin
\end{verbatim}
}
\noindent
or
{\small
\begin{verbatim}
proc??????_displ_X_it??????.bin
proc??????_displ_Y_it??????.bin
proc??????_displ_Z_it??????.bin
\end{verbatim}
}
\noindent
For elastic domains, the divergence and curl taken from the velocity (or displacement) field,
i.e. $\nabla\cdot{\bf {v}}$ and $\nabla\times{\bf {v}}$ (or $\nabla\cdot{\bf {d}}$ and $\nabla\times{\bf {d}}$), get stored
as well:
{\small
\begin{verbatim}
proc??????_div_it??????.bin
proc??????_curl_X_t??????.bin
proc??????_curl_Y_it??????.bin
proc??????_curl_Z_it??????.bin
\end{verbatim}
}
\noindent
The files denoted \texttt{\small proc??????\_div\_glob\_it??????.bin} and
\texttt{\small proc??????\_curl\_glob\_it??????.bin}
are stored on the global points only, all the other arrays are stored
on all GLL points. Note that the components X/Y/Z can change to E/N/Z
according to the
\texttt{\small SUPPRESS\_UTM\_PROJECTION}
flag (see also Appendix~\ref{cha:Coordinates} and \ref{cha:channel-codes}).
